Biotic invasions fuck with the manageability of pollination networks

### 2017-02-21 paper/supp_info_2.Rmd
Matching threshold

# S6: Using control profile heuristics

>>>>

# Matching's weight threshold

We use the frequency with which a species is classified as a driver node $f_D$ and the frequency with which a species is classified as a superior node $f_S$ in a set of accepted maximal matchings to infer their relative importance.
Maximal matchings were accepted if the matching weight was over a certain threshold. 
This threshold was defined as a proportion of the maximum matching's weight. 
Here we evaluate the impact that a particular choice of this threshold has on $f_D$ and $f_S$.

The number of accepted maximal matchings increased rapidly as the threshold at which they are accepted decreases. Nevertheless this number stabilises below approximately 0.6-0.7 (Figure \@ref(fig:fig-n-matchings)).

```{r fig-n-matchings, echo = F, message = F, warning = F, fig.width = 3.2, fig.height = 2.4, results = "hide", fig.cap= "**Number of maximal matchings as a function of the weight threshold**. Each line correspond to one network."}
d_sp %>%
	dplyr::filter(scaled == FALSE, 
								study != "ballantyne", 
								type == "asymmetry") %>%
	dplyr::group_by(net_name, threshold) %>%
	dplyr::summarise(n_matchings = mean(unique(n_matchings))) %>%
	ggplot(aes(x = threshold, y = n_matchings)) +
	geom_line(aes(group = net_name), colour = "grey20", size = 0.3) +
	scale_y_log10() +
	scale_x_reverse() +
	ylab("maximal matchings") +
	fer_theme
```

We then examined how the relative importance of species changes with the chosen threshold. 
We observe, that regardless of the matching weight's threshold species tend to be superior nodes in all or none of the matchings, which equates to $f_S$ values of one or zero, and the contrast between important and unimportant species is maintained (Figure \@ref(fig:fig-f-s-rankings)).
Contrastingly, species' $f_D$ reach intermediate levels of importance and show higher variability across thresholds (Figure \@ref(fig:fig-f-d-rankings)).

```{r fig-f-s-rankings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 9, results = "hide", fig.cap="**Frequency with which a species was classified as a superior node ($f_S$) as a function of the matching weight threshold**. Rows correspond to study sites."}
sites <- net_prop %>% dplyr::arrange(study, site, inv) %$% site %>% unique()
threshold_data <- d_sp %>%
			dplyr::filter(scaled == FALSE, 
										study != "ballantyne", 
										type == "asymmetry") %>%
			dplyr::mutate(f_s = d_freq / n_matchings, 
										f_d = (n_matchings - m_freq) / n_matchings, 
										site = factor(site, sites), 
										site_num = as.numeric(site)) %>%
			dplyr::group_by(net_name, threshold, species) %>%
			dplyr::summarise(f_s = mean(f_s),
											 f_d = mean(f_d), 
											 site = dplyr::first(site),
											 site_num = dplyr::first(site_num),
											 inv = dplyr::first(inv)) %>%
			dplyr::group_by() %>%
			dplyr::mutate(site_num = site_num -1, # to account for ballantynes
										inv = plyr::mapvalues(inv, c(T, F), 
																					c("invaded", "uninvaded")))
p <- c("f_s", "f_d") %>%
	plyr::llply(function(x){
		threshold_data %>% 
			# dplyr::group_by(net_name, species) %>%
			# dplyr::arrange(threshold) %>%
			# dplyr::mutate(initial = dplyr::first(f_s)) %>%
			# dplyr::group_by() %>%
			# reshape2::melt(measure.vars = c("f_s", "f_d"), value.name = "f") %>% 
			# dplyr::group_by() %>% View
			ggplot(aes_string(x = "threshold", y = x)) +
			geom_line(aes(group = species), size = 0.2) +
			# geom_point(size = 0.5) +
			facet_grid(site_num ~ inv) +
			fer_theme
	})

p[[1]] + ylab(expression(f[S]))
```

```{r fig-f-d-rankings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 9, results = "hide", fig.cap= "**Frequency with which a species was classified as a superior node ($f_D$) as a function of the matching weight threshold**. Rows correspond to study sites."}
p[[2]] + ylab(expression(f[D]))

Finally, we examined the agreement across thresholds by calculating the Spearman correlation matrix of species' $f_S$ and $f_D$ for each network. 
The mean of those matrices is shown in Table S4. 
Overall, among all thresholds, we found a very high agreement for $f_S$, and high to very high for $f_D$. 
With the exception of using a threshold of 1 (only maximum matchings are accepted), the choice of the threshold has little impact on the relative importance of species. 
For convenience, we use an intermediate level of 0.5. 
Nevertheless, the differences are marginal and any threshold $<= 0.9$ is likely to produce very similar results.

```{r table-correlations-thresholds, echo = F, message = F, warning = F, results = "asis", sanitize = F}
correlation_matrix <- c("f_s", "f_d") %>%
	plyr::llply(function(x){
		threshold_data %>%
			plyr::daply("net_name", get_corr_matrix, column = x) %>%
			plyr::aaply(c(2, 3), mean)
	})

correlation_matrix_o <- correlation_matrix[[1]]
correlation_matrix_o[upper.tri(correlation_matrix_o)] <- 
	correlation_matrix[[2]][upper.tri(correlation_matrix[[2]])]
c_m <- round(correlation_matrix_o, 2)
c_m[is.na(c_m)] <- "—"

xtable::xtable(c_m, caption = "\\textbf{Spearman correlation coefficient among different matching weight thresholds}. The upper triangle shows values for $f_D$ and the lower triangle shows values for $f_S$") %>%
	print(comment = FALSE, include.rownames = TRUE, caption.placement = "top")
```
